Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-09-01 ms.tex
typos in Fermi section fixed

The analysis of this work follows the same procedure as described in detail in \citet{article:Abdo_etal:2009}. To eliminate albedo gamma rays from the Earth limb, a zenith angle cut of 105$^{\circ}$ is applied. The \emph{Fermi} Science Tools version v9r23p1 and Instrumental Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events calibrated  in flight) were used throughout this work. Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful. The \emph{Fermi}-LAT collaboration estimates the systematic uncertainties at 10 GeV to be around 20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits at the 95\% confidence level in the energy range 1-100 GeV, assuming both a unresolved, point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$ and $2.5$.

>>>>

The analysis of this work follows the same procedure as described in detail in \citet{article:Abdo_etal:2009}. To eliminate albedo gamma rays from the Earth limb, a zenith angle cut of 105$^{\circ}$ is applied. The \emph{Fermi} Science Tools version v9r23p1 and Instrumental Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events calibrated  in flight) were used throughout this work. Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful. The \emph{Fermi}-LAT collaboration estimates the systematic uncertainties at 10 GeV to be around 20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved, point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and $2.5$.
